To Airbnb?: A Question of Revenue

### 2018-05-31 papers/full_paper.Rmd
Updating readme and title

---
title: "To Airbnb?: A Question of Revenue"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Greenfield Advisors and University of Melbourne"
date: "May 5th, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "To Airbnb?: A Question of Revenue"
subtitle: "Andy Krause and Gideon Aschwanden"
author: "Greenfield Advisors and University of Melbourne"
date: "May 30th, 2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
editor_options: 
  chunk_output_type: console
---
